A Review on Multi-Label Learning Algorithms

### 2018-01-14 Paper/Presentation/mll_review.tex
Update presentation

%------------------------------------------------
\subsection{Evaluation Metrics}
\begin{frame}
\frametitle{\insertsection : \insertsubsection}
Need for more complicated evaluation than traditional supervised learning(accuracy, F-measure etc). There are 2 metrics categories 
	\begin{itemize}
		\item \emph{Example-based: }Evaluates system's performance on each example and returns the mean value. 
		\begin{itemize}
			\item \emph{From classification perspective:} $Subset Accuracy$, $Hamming Loss$, $accuracy_{exam}$, $precision_{exam}$, $recall_{exam}$, $F^\beta_{exam}$
			\item \emph{From ranking perspective:} one-error, coverage, ranking loss, average precision
		\end{itemize}
		\item \emph{Label-based: }Evaluates system's performance on each class label separately and returns macro/micro averaged value across all class labels
		\begin{itemize}
			\item From classification perspective: $B_{macro}$, $B_{micro}$
			\item From ranking perspective: $AUC_{macro}$, $AUC_{micro}$
		\end{itemize}
	\end{itemize}
TODO: theoretical results?
\end{frame}
%------------------------------------------------
\section{Multi-label Learning Algorithms}
%------------------------------------------------

\subsection{Simple Categorization}

@@

Assume multi-label classification problem with $q$ possible class labels $Y=\{y_1, \dots y_q\}$

Group algorithms in two categories:
\begin{itemize}
	\item \emph{Problem Transformation Methods: }Transform the learning problem into other well-established learning scenarios (fit data to algorithm philosophy)
	\item \emph{Algorithm Adaptation Methods: }Adapt popular learning techniques to deal with multi-label data directly (fit algorithm to data philosophy)
\end{itemize}
\end{frame}
%------------------------------------------------
\subsection{Problem Transformation Methods}
%------------------------------------------------
\begin{frame}
\Huge{\centerline{Problem Transformation Methods}}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{\insertsection : \insertsubsection}
\begin{figure}
	\begin{center}
		\includegraphics[scale = 0.7]{images/pt.png}
	\end{center}
\end{figure}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Binary Relevance}

@@

Pros \& cons:
\begin{itemize}
	\item Simple, parallelizable
	\item Sensitive to class-imbalanced data
	\item Ignores label correlations (first-order method)
\end{itemize}

@@

\begin{frame}
\frametitle{Classifier chains}
\begin{itemize}
	\item High-order approach algorithm
	\item Transform the problem into a chain of binary classification problems
	\item Build subsequent binary classifiers upon the predictions of preceding ones
	\item A permutation function is used to specify an order to the labels
	\item Binary training set
constructed by appending each instance with its relevance
to those labels
	\item Predict relevant labels for unknown instances by iteratively traversing the classifier chain
\end{itemize}

Pros \& cons:
\begin{itemize}
	\item Effectiveness largely affected by the ordering
	\item Exploitation of label correlations
	\item Does not support parallel implementation
\end{itemize}
\end{frame}
%------------------------------------------------

\begin{frame}
\frametitle{Calibrated Label Ranking}
\begin{itemize}
	\item Second-order approach algorithm
	\item Transform the problem into a label ranking problem
	\item Ranking implemented by pairwise comparison techniques
	\item For $q$ labels, generate $q(q-1)/2$ binary classifiers by pairwise comparison
	\item Construct training set per label pairs considering the example's relevance
	\item For unknown instance, get the overall classifiers' votes
	\item Virtual label $y_v$ as artificial splitting point between relevant and irrelevant labels
\end{itemize}
Pros \& cons:
\begin{itemize}
	\item Smooth the class-imbalance
	\item Classifier's number grows from linear to quadratic scale
	\begin{itemize}
		\item Improvement: Exact or approximate pruning to reduce classifier's number to be queried
	\end{itemize}
\end{itemize}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Random k-Labelsets}
\begin{itemize}
	\item High-order approach algorithm
	\item Decompose to an ensemble of multi-class classification problems
	\item Each component targets a random subset of $Y$, inducing a multi-class classifier by Label Powerset (LP) techniques
	\item Convert training set into a multi-class set, treating each label set as a new class
	\item Each example is reassigned with the mapped single-label participating in multi-class classifier induction
	\item For unknown $x$, counts the maximum and actual number of votes
	\item Label set is relevant when the actual number of votes exceeds
half of the maximum ones
\end{itemize}
Pros \& cons:
\begin{itemize}
	\item Incompleteness: predicts only label sets included in the training set
	\item Inefficiency: large $Y$ implies high training complexity.Improve by invoking LP only on random k-labelsets and ensemble learning to LP classifiers
\end{itemize}
\end{frame}
%------------------------------------------------
\subsection{Alogrithm Adaptation Methods}
%------------------------------------------------
\begin{frame}
\Huge{\centerline{Algorithm Adaptation Methods}}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{\insertsection : \insertsubsection}
\begin{figure}
	\begin{center}
		\includegraphics[scale = 0.75]{images/aa.png}
	\end{center}
\end{figure}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Multi-Label k-Nearest Neighbour}
\begin{itemize}
	\item First-order approach algorithm, adapting knn techniques
	\item Lazy learning and Bayesian reasoning
	\item Maximum a posteriori (MAP) rule to make prediction by reasoning and embody label info in the neighbours
	\item For new instances, $N(x)$ represents the set of its knn (uses Euclidean distance)
	\item Posterior probability $\mathbb{P}(H_j|C_j)$ and $\mathbb{P}(\neg H_j|C_j)$, where $C_j$ is the knn of $x$ and $H_j$ is the event that $x$ has the label $y_j$
	\item Predict relevant label set based on which probability is higher(MAP rule)
	\item Frequency counting strategy:
	\begin{enumerate}
		\item Estimation of prior probabilities ($\mathbb{P}(H_j)$ \& $\mathbb{P}(\neg H_j)$) using a smoothing parameter $s$ (usually $s=1$)
		\item Estimation of likelyhoods (($\mathbb{P}(C_j|H_j)$ \& $\mathbb{P}(C_j|\neg H_j)$)
	\end{enumerate}

\end{itemize}
\end{frame}

%------------------------------------------------
\begin{frame}
\frametitle{Multi-label Decision Tree}
\begin{itemize}
	\item First-order approach algorithm, that adopts decision tree techniques
	\item ML entropy is used to
build the decision tree recursively
	\item ML dataset $T$ is divided based on a splitting value $\theta$ ($T^-$ \& $T^+$)
	\item Starting from the root, ML-DT identifies the feature and the splitting value which
maximizes the information gain and creates the two child nodes
	\item ML-DT assumes independence among labels and computes the ML
entropy in a decomposable way
	\item Any test instance allocated in a leaf node is associated with the most frequent label $y$ present in that node
\end{itemize}
Pros \& cons:
\begin{itemize}
	\item High efficiency
	\item Improvement: pruning strategy  or ensemble learning techniques
\end{itemize}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Ranking Support Vector Machine}
\begin{itemize}
	\item Second-order approach algorithm, that adopts maximum margin strategy 
	\item $q$ linear classifiers, optimized to minimize the empirical
ranking loss and enabled to handle nonlinear cases with kernel tricks 
	\item $W = {(w_j , b_j ) | 1 ≤ j ≤ q}$,where $w_j \in \mathbb{R}^d$ and
$b_j \in \mathbb{R}$ are the weight vector and bias
	\item Rank-SVM defines the learning system's
margin on ($x_i$ , $Y_i$), considering its ranking ability on the example’s relevant/irrelevant labels
\end{itemize}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Collective Multi-Label Classifier}
\begin{itemize}
	\item 
	\item 
	\item 
	\item 
\end{itemize}
\end{frame}
%------------------------------------------------
\section{Related Learning Settings}
%------------------------------------------------

\begin{frame}
\frametitle{\insertsection}
\begin{itemize}
	\item 
	\item 
	\item 
	\item 
\end{itemize}
\end{frame}

%------------------------------------------------
\section{Conclusion}
%------------------------------------------------
\begin{frame}
\frametitle{\insertsection}
\begin{itemize}
	\item 
\end{itemize}
\end{frame}

%------------------------------------------------
\section{The end}
\begin{frame}
\Huge{\centerline{Thank you}}
\end{frame}
%------------------------------------------------
\end{document}

>>>>

%------------------------------------------------
\subsection{Evaluation Metrics}
\begin{frame}
\frametitle{\insertsection : \insertsubsection}
Two categories and perspectives:
	\begin{itemize}
		\item \emph{Example-based: }Evaluates multi-labelled performance on each example, extrapolate to whole dataset
		\begin{itemize}
			\item \emph{Classification perspective:} 
				\begin{itemize}
					\item Subset Accuracy, Hamming Loss
					\item Precision, Recall, F-measure, F$^\beta$ -measure
				\end{itemize}
			\item \emph{Ranking perspective:} one-error, coverage, ranking loss, average precision
		\end{itemize}
		\item \emph{Label-based: }Evaluates performance on each label separately, extrapolate to whole label set
		\begin{itemize}
			\item Classification perspective: Macro/Micro averaging for single-label example-based, classification-based measures
			\item Ranking perspective: Macro/Micro averaging for AUC 
		\end{itemize}
	\end{itemize}
	Classifiers should aim to optimize \emph{multiple} metrics
\end{frame}
%------------------------------------------------
\section{Multi-label Learning Algorithms}
%------------------------------------------------

\subsection{Categorization}

@@

Group algorithms in two categories:
\begin{itemize}
	\item \emph{Problem Transformation Methods:}

		\begin{itemize}
			\item Transform the learning problem into other well-established learning scenarios
			\item ``Fit data to algorithm'' philosophy
		\end{itemize}

	\item \emph{Algorithm Adaptation Methods:}
		\begin{itemize}
			\item Adapt popular learning techniques to deal with multi-label data directly
			\item ``Fit algorithm to data'' philosophy
		\end{itemize}
\end{itemize}

Include algorithms that:
\begin{itemize}
	\item Has broad, unique characteristics
	\item Has primitive impact, i.e. leads to a number follow-up related methods
	\item Is influential and highly-cited in multi-label learning
\end{itemize}

\end{frame}
%------------------------------------------------
\subsection{Problem Transformation Methods}
%------------------------------------------------
\begin{frame}
\Huge{\centerline{Problem Transformation Methods}}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{\insertsection : \insertsubsection}
\begin{figure}
	\begin{center}
		\includegraphics[scale = 0.7]{images/pt.png}
	\end{center}
\end{figure}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Binary Relevance}

@@

Pros \& cons:
\begin{itemize}
	\item Simple, one-vs-rest scheme, parallelizable
	\item Sensitive to class-imbalanced data
	\item Ignores label correlations (first-order method)
\end{itemize}

@@

\begin{frame}
\frametitle{Classifier chains}
\begin{itemize}
	\item A permutation function $f_p$ is used to order $Y$
	\item Transform into a \emph{chain} of binary classification problems
	\item Enrich representations at each step $j$ by concatenating each $x_i$ with the confidence of the $j$-th classifier
	\item Predict relevant labels for unknown instances by iteratively traversing the classifier chain
\end{itemize}

Pros \& cons:
\begin{itemize}
	\item Higher-order method: exploitation of label correlations, but in a random manner
	\item Highly sensitive to $f_p$. Ensemble schemes attempt to overcome it. 
	\item Iterative operation prevents parallel implementation
\end{itemize}
\end{frame}
%------------------------------------------------

\begin{frame}
\frametitle{Calibrated Label Ranking}
\begin{itemize}
	\item Transform into a label pairwise comparison ranking problem
	\item For $q$ labels, generate $q(q-1)/2$ binary classifiers by pairwise comparison
	\item Construct training sets $D_{jk} : \{x_i | y_j \in Y_i \oplus y_k \in Y_i\}$
	\item For an unknown instance, all classifiers' votes are aggregated and ranked 
	\item A virtual label $y_v$ serves as the artificial splitting point between relevant and irrelevant labels
\end{itemize}
Pros \& cons:
\begin{itemize}
	\item Second-order approach algorithm. One-vs-one scheme.
	\item Smooths out the class-imbalance problem
	\item Number of classifiers s quadratic to $|Y|$ (compared to linear for BR) 
	\begin{itemize}
		\item Pruning methods to reduce the search space 
	\end{itemize}
\end{itemize}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Random k-Labelsets}
\begin{itemize}
	\item Decompose to an ensemble of multi-class classification problems
	\item Each component targets a random subset of $Y$, classified with Label Powerset (LP) techniques:
	\begin{itemize}
	\item Transform to single-label data by treating each distinct labelset as a new class
	\item Each example is reassigned with the mapped single-label participating in multi-class classifier induction
	\item For unknown $x$, counts the maximum and actual number of votes
	\item Label set is relevant when the number of votes exceeds half of the max
	\end{itemize}
\end{itemize}
Pros \& cons:
\begin{itemize}
	\item High-order approach algorithm
	\item Data-sensitive: Cannot generalize to labelsets not in the training set, too few examples for some labelsets
	\item Large $Y$ implies high training complexity.
	\item Improve by invoking an ensemble on random k-sized labelsets
\end{itemize}
\end{frame}
%------------------------------------------------
\subsection{Alogrithm Adaptation Methods}
%------------------------------------------------
\begin{frame}
\Huge{\centerline{Algorithm Adaptation Methods}}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{\insertsection : \insertsubsection}
\begin{figure}
	\begin{center}
		\includegraphics[scale = 0.75]{images/aa.png}
	\end{center}
\end{figure}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Multi-Label k-Nearest Neighbour}
\begin{itemize}
	\item First-order approach algorithm, adapting knn techniques
	\item Compares the MAP probabilities: $P(K|C_j), K \in \{H_j, \neg H_j\}$ 
	\item Priors $P(K)$ computed by smoothed frequency estimation in the training data 
	\item Likelihoods $P(C_j|K)$ are computed as a function of:
	\begin{itemize}
		\item $\kappa(r)$, the number of examples labelled $y_j$ with $r$ neighbours labelled $y_j$
		\item $\overset{\sim}{\kappa}(r)$, the number of examples not labelled $y_j$ with $r$ neighbours labelled $y_j$
	\end{itemize}
\end{itemize}

Pros \& cons:
\begin{itemize}
	\item First-order approach, Bayesian and Lazy reasoning
	\item Decision boundary can be modified on-line via new instances
	\item Class imbalance can be overcome by calculating priors
	\item Extensions proposed for label correlation exploitations
\end{itemize}

\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Multi-label Decision Tree}
\begin{itemize}
	\item Multi-label entropy is used to build a decision tree recursively
	\item Split position is such that the information gain criterion is maximized
	\item Dataset $T$ is split on the $l$-th feature valued $\theta$ to branches ($T^-$ \& $T^+$), where $ x_{il} \leq \theta, x_i \in T^-$ and $ x_{il} > \theta, x_i \in T^+$
	\item Recurse on subtrees until a stopping criterion is met (e.g. child size)
	\item Single-label entropy is computed by considering labelsets as new classes
	\item Assumes independence among labels to ensure low computational cost
	\item Unseen instances are assigned the label of the majority of members of the leaf they arrive
\end{itemize}
Pros \& cons:
\begin{itemize}
	\item First-order algorithm, highly efficient
	\item Assumes label independence
	\item Pruning and ensemble strategies proposed
\end{itemize}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Ranking Support Vector Machine}
\begin{itemize}
	\item $q$ linear classifiers, optimized to minimize the empirical ranking loss
	\item For each relevant-nonrelevant label pair $(y_j,y_k) \in Y_j \times \bar Y$ their decision boundary is marked by $\left<w_j,w_k\right> + b_j - b_k=0$
	\item Retrieves a ranked label pairs list for each unseen instance
	\item Non-linearity achievable through feature mapping and the kernel trick
	\item Convex quadratic programming problem, solved by any QP solver
\end{itemize}
Pros \& cons:
\begin{itemize}
	\item Second-order approach, maximum margin strategy 
	\item Extensible by kernel learning, kernel selection can be overcome by MKL techniques 
	\item Adaptable learning by selecting an appropriate loss function
\end{itemize}

\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Collective Multi-Label Classifier}
\begin{itemize}
	\item Labels encoded as binary random vectors into a joint pdf
	\item Label correlations encoded into the joint pdf as constraints
	\item Model via the maximum information entropy criterion: $H_p(x, y)$, subject to constraints $\mathbb{E_p}[f_k(x,y)] = F_k$, where $F_k$ are estimated from the training set
	\item Objective arrived by Lagrange multipliers, solvable by any constraint optimization solver
	\item Unseen instances labelled with $Y = \underset{y}{\text{argmax }} P(y | x)$
\end{itemize}
Pros \& cons:
\begin{itemize}
	\item Second-order approach. All label pairs considered, not just relevant-irrelevant ones.
	\item Intractable $\text{argmax}$ operation for a large label space without pruning.
\end{itemize}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{\insertsection : Summary}
\begin{figure}
	\begin{center}
		\includegraphics[scale = 0.45]{images/summary.png}
		\caption{Summary of Representative Multi-Label Learning Algorithms}
	\end{center}
\end{figure}
\end{frame}
%------------------------------------------------
\section{Related Learning Settings}
%------------------------------------------------
\begin{frame}
\frametitle{\insertsection}
\begin{itemize}
	\item Multi-instance learning
	\begin{itemize}
		\item Each ML example described by a bag of instances while associated with a single/binary label
		\item Models the object’s complex semantics in input space, rather than its output
	\end{itemize}
	\item Ordinal classification
	\begin{itemize}
		\item Model class co-relevance in a (vague) graded membership vector
		\item Transform ML problem to a set of ordinal set of problems
	\end{itemize}
	\item Multi-task learning
	\begin{itemize}
		\item Multiple tasks trained in parallel, sharing information
		\item Knowledge from related tasks used as an inductive bias to improve generalization 
		\item Shared or different feature space, small task workload
	\end{itemize}
	\item Data streams classification
	\begin{itemize}
		\item Real-world objects are generated online and processed in  real-time 
		\item Concept drift problem
	\end{itemize}
\end{itemize}
\end{frame}

%------------------------------------------------
\section{Conclusion}
%------------------------------------------------
\begin{frame}
\Huge{\centerline{Conclusion}}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{\insertsection : Online resources}
\begin{figure}
	\begin{center}
		\includegraphics[scale = 0.47]{images/online.png}
		\caption{Online Resources for Multi-Label Learning}
	\end{center}
\end{figure}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{\insertsection}
Summary:
\begin{itemize}
	\item Multi-label learning problem definition 
	\item Multi-label learning representative algorithms
	\item Related learning settings
\end{itemize}

Future goals:
\begin{itemize}
	\item Holy grail: Formal characterization on the underlying concept / mechanism on the appropriate usage of label correlations, especially on large output spaces
	\item Thorough experimental comparative study to discover to pros and cons of different multi-label learning algorithms
\end{itemize}
\end{frame}

%------------------------------------------------
\section{The end}
\begin{frame}
\Huge{\centerline{Thank you}}
\Huge{\centerline{Questions?}}
\end{frame}
%------------------------------------------------
\end{document}
